Supplementary materials

### 2019-11-16 manuscript/supplemental.Rmd
path updates, legend

```{r, include=F}
map <- knitr::include_graphics(here::here("manuscript/figs/map.png"))
field <- read_csv(here::here("data/02_tidied/tidied_field.csv"))
field_photos <- knitr::include_graphics(here::here("manuscript/figs/S3_site_field_photos/field_collage.png"))
micro_photos <- knitr::include_graphics(here::here("manuscript/figs/S4_site_micro_photos/micro.png"))
s18 <- include_graphics(here("manuscript/figs/18s_algae_rel_abund.png"))
tree <- include_graphics(here("manuscript/figs/otu_tree.png"))
tree_taxonomy <- include_graphics(here("manuscript/figs/taxonomy_tree.png"))
diversity <- include_graphics(here("manuscript/figs/diversity.png"))
cellct <- include_graphics(here("manuscript/figs/supp/cellct/cellct.png"))

map_cap <- "S1. Map showing locations of snow algae sampling locations in summer 2018."
table_cap <- "S2. Table of sample site information of sequenced snow algae samples."
field_photo_cap <- "S3. Photos of snow algae field sites."
micro_cap <- "Microphotos of snow algae samples included in sequencing run."
s18_cap <- "Relative abundance barplot of 18S amplicon library"
tree_cap <- "Maximum likelihood tree of rbcL amplicon library. Colors represent OTU assignments."
tax_tree_cap <- "Maximum likelihood tree of rbcL amplicon library. Colors represent taxonomic assignments."
diversity_cap <- "A. Shannon diversity of snow algae samples, plotted against sample elevation. Smooth method = linear model. B. Faith's phylogenetic diversity plotted against sample elevation."
(ref:cellct_cap) "Heatmap showing cell count relative abundance from 117 snow algae samples. Cb = Chlainomonas cf. brevispina, Ck=Chloromonas krienitzii, Cn=Chloromonas cf. nivalis, Cr=Chlainomonas rubra, G=green cells, O=other, Sn=Sanguina nivaloides"
```

>>>>

```{r, include=F}
map <- knitr::include_graphics(here::here("manuscript/figs/map.png")) # crop zoom, city font white, each site gets one point with box specifying elev range, n samples, dates, 
field_tbl <- read_csv(here::here("data/02_tidied/tidied_field.csv")) #
field_photos <- knitr::include_graphics(here::here("manuscript/figs/supp/field_photos/field_collage.png"))
micro_photos <- knitr::include_graphics(here::here("manuscript/figs/S4_site_micro_photos/micro.png"))
cellct <- include_graphics(here("manuscript/figs/supp/cellct_scatterpie/cellct_scatterpie.png")) # make pies circles circular! they're shightly squished lengthwise
tree_otu <- include_graphics(here("manuscript/supp/figs/otu_tree.png"))
tree_taxonomy <- include_graphics(here("manuscript/figs/supp/taxonomy_tree.png"))
diversity <- include_graphics(here("manuscript/figs/supp/diversity.png"))
depth <- include_graphics(here("manuscript/figs/supp/depth/depth_polished.png")) ###

map_cap <- "Map showing locations of snow algae sampling locations in summer 2018."
table_cap <- "Table of sample site information of sequenced snow algae samples."
field_photo_cap <- "Photos of snow algae field sites, arranged from high to low elevation from top to bottom. Alphanumeric code in upper left indicates sample ID."
micro_photo_cap <- "Microphotos of snow algae samples included in sequencing run."
cellct_cap <- "Proportional abundance of snow algae cell morphologies, plotted against date and elevation."
tree_cap <- "Maximum likelihood tree of rbcL amplicon library. Colors represent OTU assignments."
tax_tree_cap <- "Maximum likelihood tree of rbcL amplicon library. Colors represent taxonomic assignments."
diversity_cap <- "A. Shannon diversity of snow algae samples, plotted against sample elevation. Smooth method = linear model. B. Faith's phylogenetic diversity plotted against sample elevation."
depth_cap <- "A. Representative field photo of snow runnel, with orange on surface and green below. B. Microphoto of orange snow on surface of sample S9.1. C. Microphoto of snow algae below surface of sample S9.1. D. Relative abundance barplot of OTUs in three snow runnels. Sample H2.10 depth and surface samples were taken 1 week apart, other depth/surface pairs are from the same date."
```
